The Astropy Project

### 2017-10-26 main.tex
links

Modeling also supports a plugin system for fitters, which allows using the astropy models with external fitters. An example of this is SABA (link), which is a bridge between Sherpa (link) and astropy.modeling, to bring the Sherpa fitters into astropy.

>>>>

Modeling also supports a plugin system for fitters, which allows using the
astropy models with external fitters. An example of this is
SABA\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
and astropy.modeling, to bring the Sherpa fitters into astropy.
